method

### 2021-12-09 06_Paper/ER-ED/method.Rmd
added ED data frame

data_ED = data.frame(ID = character(), step = double(), choice = character(),
                           LBvalue = double(), LBlevel = double(), RBvalue = double(), RBlevel = double())
data_choice = data.frame(ID = character(), choice = double())

@@

# store ED data in data_ED frame
#for (i in 1:length(datalist_ED)) {

#  tmp = data.frame(datalist_ED[[i]][["participant"]][2:length(datalist_ED[[i]][["participant"]])],
#                          datalist_ED[[i]][["EDround.thisN"]][2:length(datalist_ED[[i]][["EDround.thisN"]])],
#                          datalist_ED[[i]][["EDclick.clicked_name"]][2:length(datalist_ED[[i]][["EDclick.clicked_name"]])],
#                          datalist_ED[[i]][["EDleftbutton.value"]][2:length(datalist_ED[[i]][["EDleftbutton.value"]])],
#                          datalist_ED[[i]][["EDleftbutton.nback"]][2:length(datalist_ED[[i]][["EDleftbutton.nback"]])],
#                          datalist_ED[[i]][["EDrightbutton.value"]][2:length(datalist_ED[[i]][["EDrightbutton.value"]])],
#                          datalist_ED[[i]][["EDrightbutton.nback"]][2:length(datalist_ED[[i]][["EDrightbutton.nback"]])])
#}

>>>>

data_ED = data.frame(ID = character(), step = double(), choice = character(),
                     LBvalue = double(), LBlevel = double(), RBvalue = double(), RBlevel = double())

data_choice = data.frame(ID = character(), choice = double())

@@

# store ED data in data_ED frame
for (i in 1:length(datalist_ED)) {

  tmp = data.frame(datalist_ED[[i]][["participant"]][2:length(datalist_ED[[i]][["participant"]])],
                   datalist_ED[[i]][["EDround.thisN"]][2:length(datalist_ED[[i]][["EDround.thisN"]])],
                   datalist_ED[[i]][["EDclick.clicked_name"]][2:length(datalist_ED[[i]][["EDclick.clicked_name"]])],
                   datalist_ED[[i]][["EDleftbutton.value"]][2:length(datalist_ED[[i]][["EDleftbutton.value"]])],
                   datalist_ED[[i]][["EDleftbutton.nback"]][2:length(datalist_ED[[i]][["EDleftbutton.nback"]])],
                   datalist_ED[[i]][["EDrightbutton.value"]][2:length(datalist_ED[[i]][["EDrightbutton.value"]])],
                   datalist_ED[[i]][["EDrightbutton.nback"]][2:length(datalist_ED[[i]][["EDrightbutton.nback"]])])

  colnames(tmp) = names(data_ED)
  data_ED = rbind(data_ED, tmp)
}
